\documentclass{letter}

\name{Giglium, Inc.}
\signature{ Francesco Antonio Migliorin
	\\Cell: 123.456.7890 
	\\Email: francesco.migliorin@giglium.com}
\address
{
Giglium, Inc.
\\Via Trieste 63 
\\35121 Padova (PD)
\\https://www.giglium.com
}

\begin{document}
	
	\begin{letter}
		{
			Stuart Flatow, Vice President, Safety \& Training
			\\Propane Education \& Research Council
			\\1140 Connecticut Ave. NW, Suite 1075
			\\Washington, DC 20036
		}
		
		\opening{Dear Flatow,}
		
		Giglium, Inc.\ is pleased to submit its technical and cost proposal through this letter to
		Propane Education \& Research Council in response to the Request for Proposal (RFP)
		for the Development and Support of the CETP e-learning Help Desk. Giglium has successfully demonstrated that it is a trusted and reliable vendor and partner all over the world. We are tremendously proud of the impacts that we have made in helping our clients to improve their business. For the past 5+ years, Giglium has sold over \$6 million of its products and services and it is in partnership with seven companies that are the leader in their sectors.
		
		We believe that our response meets the requirements as called out. If the Propane Education \& Research Council
		determines that Giglium’s response is deficient in any way, Giglium respectfully requests to be promptly
		notified and be given the opportunity to correct any such deficiency. Please forward any questions
		regarding this solicitation response to me. My contact information is provided below.
		On behalf of Giglium, thank you for giving us the opportunity to respond to this RFP and we look forward to
		continuing a mutually rewarding partnership.
		
		\closing{Sincerely,}
		
	\end{letter}
\end{document}
